### 2021-01-25 README.Rmd
Rebuilt README

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex,
    census_2 = census_2_ex %>% filter(!str_detect(codes, "R")),
    id = "ID"
    ) %>%
  mutate(sp = to_any_case(sp) %>% factor())
```

@@

Next we add information pertaining to our spatial cross-validation scheme. We first manually define the spatial blocks that will act as our cross-validation folds and convert them to an `sf` object using `sf_polygon()` function from the `sfheaders` package.

@@

blocks <- bind_rows(
  sf_polygon(fold1),
  sf_polygon(fold2)
) %>%
  mutate(foldID = c(1, 2))
```

@@

```{r}
SpatialBlock_ex <- spatialBlock(
  speciesData = growth_ex, k = 2, selection = "systematic", blocks = blocks,
  showBlocks = FALSE, verbose = FALSE
)

@@

We also extract the spatial cross-validation grid itself as an `sf` object for later use.

```{r}
cv_grid_sf_ex <- SpatialBlock_ex$blocks %>%
  st_as_sf()
ggplot() +
  geom_sf(data = cv_grid_sf_ex)
```

@@

```{r}
base_plot + 
  geom_sf(data = growth_ex, aes(col = buffer, shape = foldID), size = 2) +
  geom_sf(data = blocks, fill = "transparent", col = "orange")
```

@@

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, cv_grid_sf = cv_grid_sf_ex, id = "ID")
focal_vs_comp_ex
```

@@

```{r}
focal_vs_comp_ex %>% 
  unnest(cols = "comp")
```

>>>>

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex,
    census_2 = census_2_ex %>% filter(!str_detect(codes, "R")),
    id = "ID"
    ) %>%
  mutate(sp = snakecase::to_any_case(sp) %>% factor())
```

@@

Next we add information pertaining to our spatial cross-validation scheme. We first manually define the spatial blocks that will act as our cross-validation folds and convert them to an `sf` object.

@@

blocks_ex <- bind_rows(
  sfheaders::sf_polygon(fold1),
  sfheaders::sf_polygon(fold2)
) %>%
  mutate(folds = c(1, 2) %>% factor())
```

@@

```{r}
SpatialBlock_ex <- blockCV::spatialBlock(
  speciesData = growth_ex, k = 2, selection = "systematic", blocks = blocks_ex,
  showBlocks = FALSE, verbose = FALSE
)

@@

@@

```{r}
base_plot + 
  geom_sf(data = growth_ex, aes(col = buffer, shape = foldID), size = 2) +
  geom_sf(data = blocks_ex, fill = "transparent", col = "orange")
```

@@

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, cv_grid_sf = blocks_ex, id = "ID")
focal_vs_comp_ex
```

@@

```{r}
focal_vs_comp_ex %>% 
  tidyr::unnest(cols = "comp")
```
